---
title: "DGEF_Behavioral_analyses"
author: "Davide Gheza"
date: "28 March 2019"
output: pdf_document
---


```{r setup_environment,echo=FALSE,warning=FALSE,message=FALSE}

# Setup working environment
# dev.off() # clear plots
rm(list=ls()) # clear environment
cat("\014") # clear console
set.seed(42) # specify seed for RNG and ensure reproducible results
#load packages and install them if they're not
if (!require("pacman")) install.packages("pacman")
pacman::p_load(plyr, reshape2, Rmisc,ggplot2, ez, schoRsch, pastecs, MBESS,BayesFactor)
if (!require("gapminder")) install.packages("gapminder")
if (!require("dplyr")) install.packages("dplyr")
if (!require("tidyverse")) install.packages("tidyverse")
if (!require("Hmisc")) install.packages("Hmisc")
if (!require("BayesFactor")) install.packages("BayesFactor")
if (!require("reshape")) install.packages("reshape")
if (!require("sjstats")) install.packages("sjstats")
if (!require("sjPlot")) install.packages("sjPlot")
if (!require("lme4")) install.packages("lme4")

library(gapminder)
library(dplyr)
library(tidyverse)
library(Hmisc)
library(reshape)
library(sjstats)
library(sjPlot)
library(lme4)
library(interactions)
```



```{r Import data, echo=FALSE, results="hide"}
## Import data

wd <- ("C:/Users/gdavide/Documents/Pourtois/Master student supervision/DGEF/analyses/")
setwd(wd) # set work directory

# DGEF data
raw <- read.csv2("79.csv",header=TRUE,na.strings="NaN") # read data DGEF

raw$Condition = as.factor(raw$Condition)

# filter out practice and instructions
expdata = raw[(raw$Running.Trial. %in% "ExperimentList"),]

# Questionnaires - BisBas, NeedForCognition
quest <- read.csv2("DGEF_Q_79.csv",header=TRUE,na.strings="NaN") # read data questionnaires

```
```{r Questionnaires}
## Questionnaires
## BISBAS
quest.bisbas = quest[(quest$Procedure.Block. %in% "QBISBAS"),]
# revert scores for items except 2,22 - 4 opt likert, range 0-3
quest.bisbas$ItemdisplayBISBAS.RESP[!(quest.bisbas$ItemsBISBAS %in% c(2,22))] = 3-quest.bisbas$ItemdisplayBISBAS.RESP[!(quest.bisbas$ItemsBISBAS %in% c(2,22))]
# define subscales by item
quest.bas.drive = quest.bisbas[(quest.bisbas$ItemsBISBAS %in% c(3, 9, 12, 21)),]
quest.bas.fun = quest.bisbas[(quest.bisbas$ItemsBISBAS %in% c(5, 10, 15, 20)),]
quest.bas.reward = quest.bisbas[(quest.bisbas$ItemsBISBAS %in% c(4, 7, 14, 18, 23)),]
quest.bis = quest.bisbas[(quest.bisbas$ItemsBISBAS %in% c(2, 8, 13, 16, 19, 22, 24)),]
# individual score for subscale
bas.drive.subj = group_by(quest.bas.drive, Subject)
bas.drive.subj = summarise(bas.drive.subj,
                           sumscore = sum(ItemdisplayBISBAS.RESP))
bas.fun.subj = group_by(quest.bas.fun, Subject)
bas.fun.subj = summarise(bas.fun.subj,
                           sumscore = sum(ItemdisplayBISBAS.RESP))
bas.reward.subj = group_by(quest.bas.reward, Subject)
bas.reward.subj = summarise(bas.reward.subj,
                           sumscore = sum(ItemdisplayBISBAS.RESP))
bis.subj = group_by(quest.bis, Subject)
bis.subj = summarise(bis.subj,
                           sumscore = sum(ItemdisplayBISBAS.RESP))

## NFC
quest.nfc = quest[(quest$Procedure.Block. %in% "QNFC"),]
# revert scores for items 3,4,5,7,8,9,12,16,17 - 5 opt likert, range 0-4
quest.nfc$ItemdisplayNFC.RESP[(quest.nfc$ItemsNFC %in% c(3,4,5,7,8,9,12,16,17))] = 4-quest.nfc$ItemdisplayNFC.RESP[(quest.nfc$ItemsNFC %in% c(3,4,5,7,8,9,12,16,17))]
# individual score 
nfc.subj = group_by(quest.nfc, Subject)
nfc.subj = summarise(nfc.subj,
                     sumscore = sum(ItemdisplayNFC.RESP))

## dataframe with all questionnaire's individual scores
# bind the scales together
quest.subj = rbind(bas.drive.subj,bas.fun.subj,bas.reward.subj,bis.subj,nfc.subj)
# add scale name variable 
quest.subj$scale = rep(c("drive","fun","reward","bis","NFC"),   
                                       each = length(unique(quest.subj$Subject)))
# wide format
quest.subj.wide = dcast(quest.subj, Subject ~ scale, value.var="sumscore")
  
## plot

  #plot correlation
  quest.subj.wide %>%
    ggplot(aes(x = NFC, y = bis)) +
    geom_point() +
    geom_smooth(method=lm, se=TRUE, fullrange=TRUE) +
    theme(axis.text = element_text(size = 16),
          axis.title = element_text(size = 16))

  # plot violin
  quest.subj %>%
    ggplot(aes(x = scale, y = sumscore)) +
    geom_point() +
    geom_violin(mapping = NULL, data = NULL, stat = "ydensity",
                position = "dodge", draw_quantiles = NULL, trim = TRUE,
                scale = "area", na.rm = FALSE, show.legend = NA, inherit.aes = TRUE) + 
    stat_summary(fun.y=mean, geom="point", shape=20, size=5) +
    geom_jitter(shape=16, position=position_jitter(0.02), size=1) +
    theme(axis.text = element_text(size = 16),
          axis.title = element_text(size = 16))

```

```{r FB ratings - guessing}
## FB ratings - after guessing

#filter FbRateProc

expdata.FbRate = expdata[(expdata$Procedure.SubTrial. %in% "FbRateProc"),]

# sort by sbj and cond
expdata.FbRate = expdata.FbRate[order(expdata.FbRate$Subject, expdata.FbRate$Condition),] 

# subset 
expdata.FbRate = subset(expdata.FbRate, select = c(Subject, Condition, FbRateXa, FbRateXf, FbRateXr))

# add FBrate repetition n. (note: 10 rating)

expdata.FbRate$rateRep = rep((1:10), times = ((length(unique(expdata.FbRate$Subject)))*
                                               (length(unique(expdata.FbRate$Condition))))
                             )

# compute VAS as percentage (relative to pixel range)
expdata.FbRate$VASa = (expdata.FbRate$FbRateXa-316)/396*100
expdata.FbRate$VASf = (expdata.FbRate$FbRateXf-316)/396*100
expdata.FbRate$VASr = (expdata.FbRate$FbRateXr-316)/396*100

# invert score for Frustrerend

expdata.FbRate$VASf = 100-expdata.FbRate$VASf

# long format: RateType as condition

expdata.FbRate = gather(expdata.FbRate, key = "RateType", value = "percent", VASa:VASr)
expdata.FbRate = subset(expdata.FbRate, select = c(Subject, Condition, rateRep, RateType, percent)) # drop raw rates

# create factor outcome

expdata.FbRate$outcome[(expdata.FbRate$Condition %in% c("31","51"))] = "reward"
expdata.FbRate$outcome[(expdata.FbRate$Condition %in% c("32","52"))] = "noreward"

expdata.FbRate$outcome = as.factor(expdata.FbRate$outcome)

# create factor effortlevel

expdata.FbRate$efflev[(expdata.FbRate$Condition %in% c("31","32"))] = "low"
expdata.FbRate$efflev[(expdata.FbRate$Condition %in% c("51","52"))] = "high"

expdata.FbRate$efflev = as.factor(expdata.FbRate$efflev)

## combine expdata.FbRate with questionnaires' individual scores
expdata.FbRate = merge(expdata.FbRate, quest.subj.wide)
# center questionaires
expdata.FbRate$drive = scale(expdata.FbRate$drive, center=TRUE, scale=FALSE)
expdata.FbRate$fun = scale(expdata.FbRate$fun, center=TRUE, scale=FALSE)
expdata.FbRate$reward = scale(expdata.FbRate$reward, center=TRUE, scale=FALSE)
expdata.FbRate$bis = scale(expdata.FbRate$bis, center=TRUE, scale=FALSE)
expdata.FbRate$NFC = scale(expdata.FbRate$NFC, center=TRUE, scale=FALSE)

## exclude sbj with out-of-scale FB rating
# FbRate.blacklist = unique(expdata.FbRate$Subject[(expdata.FbRate$percent > 110 | expdata.FbRate$percent < -10)])
# expdata.FbRate = expdata.FbRate[!(expdata.FbRate$Subject %in% FbRate.blacklist),]

## plot FbRate for cond against questionnaire score (warning: merging all RateTypes)
expdata.FbRate %>%
    ggplot(aes(x = NFC, y = percent, color=Condition)) +
    geom_point() +
    geom_smooth(method=lm, se=FALSE, fullrange=TRUE, aes(fill=Condition)) +
    theme(axis.text = element_text(size = 16),
          axis.title = element_text(size = 16),
          legend.title = element_text(size=14),
          legend.text = element_text(size=14),
          plot.title = element_text(size = 16)) +
    labs(title="NFC vs. FB rate", x = "NFC", y = "FB rate")


### inspect single subject ratings ###
expdata.FbRate %>% 
  mutate(label = paste0(expdata.FbRate$Condition, expdata.FbRate$RateType)) %>%  # create label defining single levels by RateType*Outcome*Effort
  filter(Subject == 1) %>%                                                        # filter sbj n
  ggplot(aes(x = label, y = percent)) +
    geom_point() +
    geom_violin(mapping = NULL, data = NULL, stat = "ydensity",
                position = "dodge", draw_quantiles = NULL, trim = TRUE,
                scale = "area", na.rm = FALSE, show.legend = NA, inherit.aes = TRUE) +
    stat_summary(fun.y=mean, geom="point", shape=4, size=10, color="black") +
    geom_jitter(shape=16, position=position_jitter(0.02), size=2) +
    theme(axis.text = element_text(size = 16),
          axis.title = element_text(size = 16))  





## Exporting FB rating - sbj level AVERAGES by Condition and RateType ##

# set up data frame for by-group processing 
FbRate.subj = group_by(expdata.FbRate, Condition, Subject, RateType)

# calculate the summary metrics - mean for Subject*Condition*RateType
FbRate.subj = summarise(FbRate.subj,
                        VAS.mean = mean(percent))


### exclude sbj with out-of-scale FB rating - based on mean for Subject*Condition*RateType ###
FbRate.blacklist = unique(FbRate.subj$Subject[(FbRate.subj$VAS.mean > 105 | FbRate.subj$VAS.mean < -5)])
expdata.FbRate = expdata.FbRate[!(expdata.FbRate$Subject %in% FbRate.blacklist),]
FbRate.subj = FbRate.subj[!(FbRate.subj$Subject %in% FbRate.blacklist),] # kick out from averages data
expdata = expdata[!(expdata$Subject %in% FbRate.blacklist),] # kick out from original dataset



# save out expdata.FbRate (with inverted score for Frustrerend)
  # wide format
  FbRate.subj$widecond = paste0(FbRate.subj$Condition, FbRate.subj$RateType)
  FbRate.subj.wide = cast(FbRate.subj, Subject ~ widecond, value = "VAS.mean")
  # write.csv
  # write.csv(FbRate.subj.wide, file = "23_behavioral_FBrate_summarised_invertedFrustrerend.csv")

# log transform for non-normal distributed data

# ## set negative values as 0.1 (out of scale ratings)
# FbRate.subj$VAS.mean[FbRate.subj$VAS.mean<0] = 0.1
# ## log transform
# FbRate.subj$VAS.mean = log(FbRate.subj$VAS.mean,base= exp(10))


############# plotting FB rating - sbj level averages #############

FbRate.subj$Condition = as.factor(FbRate.subj$Condition)

FbRate.subj$RateType = as.factor(FbRate.subj$RateType)

FbRate.subj$label = paste0(FbRate.subj$Condition, FbRate.subj$RateType)

FbRate.subj$label = factor(FbRate.subj$label, 
                       levels = c("31VASa", "51VASa", "31VASf", "51VASf", "31VASr", "51VASr","32VASa", "52VASa", "32VASf", "52VASf", "32VASr", "52VASr"),            # specify levels in the order to be plotted
                       labels=c("Easy reward A", "Hard reward A", "Easy reward F", "Hard reward F", "Easy reward R", "Hard reward R", "Easy no-reward A", "Hard no-reward A", "Easy no-reward F", "Hard no-reward F", "Easy no-reward R", "Hard no-reward R"))  


# reward

FbRate.subj.reward = FbRate.subj[(FbRate.subj$Condition %in% c("31", "51")),]

FbRate.subj.reward = group_by(FbRate.subj.reward, Condition, Subject, RateType)

FbRate.subj.reward %>%
  ggplot(aes(x = label, y = VAS.mean)) +
  geom_point() +
  geom_violin(mapping = NULL, data = NULL, stat = "ydensity",
              position = "dodge", draw_quantiles = NULL, trim = TRUE,
              scale = "area", na.rm = FALSE, show.legend = NA, inherit.aes = TRUE) +
  stat_summary(fun.y=mean, geom="point", shape=4, size=10, color="black") +
  geom_jitter(shape=16, position=position_jitter(0.02), size=2) +
  theme(axis.text = element_text(size = 10),
        axis.title = element_text(size = 16))


# no-reward

FbRate.subj.noreward = FbRate.subj[(FbRate.subj$Condition %in% c("32", "52")),]

FbRate.subj.noreward = group_by(FbRate.subj.noreward, Condition, Subject, RateType)

FbRate.subj.noreward %>%
  ggplot(aes(x = label, y = VAS.mean)) +
  geom_point() +
  geom_violin(mapping = NULL, data = NULL, stat = "ydensity",
              position = "dodge", draw_quantiles = NULL, trim = TRUE,
              scale = "area", na.rm = FALSE, show.legend = NA, inherit.aes = TRUE) +
  stat_summary(fun.y=mean, geom="point", shape=4, size=10, color="black") +
  geom_jitter(shape=16, position=position_jitter(0.02), size=2) +
  theme(axis.text = element_text(size = 10),
        axis.title = element_text(size = 16))
```
```{r FB ratings - arithmetic}
## FB ratings - after effort (arithmetic)

#filter FbRateProc

expdata.EffFbRate = expdata[(expdata$Procedure.LogLevel5. %in% "EffFbRateProc"),]

# sort by sbj and cond
expdata.EffFbRate = expdata.EffFbRate[order(expdata.EffFbRate$Subject, expdata.EffFbRate$Condition),] 

# subset 
expdata.EffFbRate = subset(expdata.EffFbRate, select = c(Subject, Condition, EffFbRateXa, EffFbRateXf, EffFbRateXr))

# # add EffFBrate repetition n. (note: 13 rating, possibly less due to no rating for unaccurate resp)
# 
# expdata.EffFbRate$rateRep = rep((1:13), times = ((length(unique(expdata.EffFbRate$Subject)))*
#                                                (length(unique(expdata.EffFbRate$Condition))))
#                              )

# compute VAS as percentage (relative to pixel range)
expdata.EffFbRate$VASa = (expdata.EffFbRate$EffFbRateXa-316)/396*100
expdata.EffFbRate$VASf = (expdata.EffFbRate$EffFbRateXf-316)/396*100
expdata.EffFbRate$VASr = (expdata.EffFbRate$EffFbRateXr-316)/396*100

# invert score for Frustrerend

expdata.EffFbRate$VASf = 100-expdata.EffFbRate$VASf

# long format: RateType as condition

expdata.EffFbRate = gather(expdata.EffFbRate, key = "RateType", value = "percent", VASa:VASr)
expdata.EffFbRate = subset(expdata.EffFbRate, select = c(Subject, Condition, RateType, percent)) # drop raw rates


# create factor effortlevel

expdata.EffFbRate$efflev[(expdata.EffFbRate$Condition %in% c("22"))] = "low"
expdata.EffFbRate$efflev[(expdata.EffFbRate$Condition %in% c("42"))] = "high"

expdata.EffFbRate$efflev = as.factor(expdata.EffFbRate$efflev)


############# Exporting Eff FB rating - sbj level AVERAGES by Condition and RateType #############

# set up data frame for by-group processing 
EffFbRate.subj = group_by(expdata.EffFbRate, Condition, Subject, RateType)

# calculate the summary metrics - mean for Subject*Condition*RateType
EffFbRate.subj = summarise(EffFbRate.subj,
                        VAS.mean = mean(percent))

############# plotting Eff FB rating - sbj level averages #############

EffFbRate.subj$Condition = as.factor(EffFbRate.subj$Condition)

EffFbRate.subj$RateType = as.factor(EffFbRate.subj$RateType)

EffFbRate.subj$label = paste0(EffFbRate.subj$Condition, EffFbRate.subj$RateType)

EffFbRate.subj$label = factor(EffFbRate.subj$label, 
                       levels = c("22VASa", "42VASa", "22VASf", "42VASf", "22VASr", "42VASr"), # specify levels in the order to be plotted
                       labels=c("Easy correct A", "Hard correct A", "Easy correct F", "Hard correct F", "Easy correct R", "Hard correct R"))  


# plot (correct only)


EffFbRate.subj = group_by(EffFbRate.subj, Condition, Subject, RateType)

EffFbRate.subj %>%
  ggplot(aes(x = label, y = VAS.mean)) +
  geom_point() +
  geom_violin(mapping = NULL, data = NULL, stat = "ydensity",
              position = "dodge", draw_quantiles = NULL, trim = TRUE,
              scale = "area", na.rm = FALSE, show.legend = NA, inherit.aes = TRUE) +
  stat_summary(fun.y=mean, geom="point", shape=4, size=10, color="black") +
  geom_jitter(shape=16, position=position_jitter(0.02), size=2) +
  theme(axis.text = element_text(size = 10),
        axis.title = element_text(size = 16))

```

########################################################################################


# stats on FBratings (single rating level)          

```{r}
########## Bayesian model comparison ##############

# centering
expdata.FbRate$percent = scale(expdata.FbRate$percent, center = TRUE, scale = FALSE) #scale=TRUE -> Z points

library(BayesFactor)

num.iter=10000 # number of MonteCarlo iterations (default: 10000)

# as factor
expdata.FbRate$rateRep = as.factor(expdata.FbRate$rateRep)
expdata.FbRate$RateType = as.factor(expdata.FbRate$RateType)

## Specification of random effects
# 1) Subject*RateType = random intercept for Subject, random effect of RateType, random effect of RateType for each sbj


# Assuming a medium Cauchy prior d~Cauchy(0,.707):
m.null=lmBF(percent ~ 1 + Subject*RateType,
            data=expdata.FbRate,iterations=num.iter,whichRandom=c("Subject*RateType"),
            rscaleRandom="nuisance",rscaleFixed=.707)
m.outcome=lmBF(percent ~ Subject*RateType + outcome,
               data=expdata.FbRate,iterations=num.iter,whichRandom=c("Subject*RateType"),
               rscaleRandom="nuisance",rscaleFixed=.707)
m.efflev=lmBF(percent ~ Subject*RateType + efflev,
              data=expdata.FbRate,iterations=num.iter,whichRandom=c("Subject*RateType"),
              rscaleRandom="nuisance",rscaleFixed=.707)
m.maineffects=lmBF(percent ~ Subject*RateType + outcome + efflev,
                   data=expdata.FbRate,iterations=num.iter,whichRandom=c("Subject*RateType"),
                   rscaleRandom="nuisance",rscaleFixed=.707)
m.interaction=lmBF(percent ~ Subject*RateType + outcome * efflev,
                   data=expdata.FbRate,iterations=num.iter,whichRandom=c("Subject*RateType"),
                   rscaleRandom="nuisance",rscaleFixed=.707)
m.interactionNFC=lmBF(percent ~ Subject*RateType + outcome * efflev * NFC,
                   data=expdata.FbRate,iterations=num.iter,whichRandom=c("Subject*RateType"),
                   rscaleRandom="nuisance",rscaleFixed=.707)
```
# BF model x | null

```{r}
m.outcome/m.null
m.efflev/m.null
m.maineffects/m.null
m.interaction/m.null
m.interactionNFC/m.null
```
# BF model x | model y

```{r}
m.interactionNFC/m.interaction
m.interactionNFC/m.maineffects
m.interactionNFC/m.efflev
m.interactionNFC/m.outcome
m.interactionNFC/m.null



# chains = posterior(m.interaction, iter=10000)
# summary(chains)

# plot(m.interaction, include1=FALSE, addDenom = FALSE)
# ?plot


```
--> the interaction model is the best one. 

--> the interaction model is the best one. This interaction can be interpreted as 
"Participant rated the reward FB as more pleasant when they anticipated high vs low cognitive effort, 
or they rated the no-reward FB as more pleasant when they anticipated low vs high cognitive effort"



# Direction of interaction: t-test between effort levels, within each reward level

```{r}

# reward easy less pleasant than reward hard ( <0 )
bf.reward = ttestBF(x = expdata.FbRate$percent[(expdata.FbRate$Condition %in% "31")],
                    y = expdata.FbRate$percent[(expdata.FbRate$Condition %in% "51")],
                    paired = TRUE, nullInterval = c(-Inf,0))

# noreward easy more pleasant than noreward hard ( >0 )
bf.noreward = ttestBF(x = expdata.FbRate$percent[(expdata.FbRate$Condition %in% "32")],
                      y = expdata.FbRate$percent[(expdata.FbRate$Condition %in% "52")],
                      paired = TRUE, nullInterval = c(0,Inf))

bf.reward
bf.noreward

```

# same as before, but on averages across rate repetitions - should I average across rate type??
```{r}

# reward easy less pleasant than reward hard ( <0 )
bf.reward = ttestBF(x = FbRate.subj$VAS.mean[(FbRate.subj$Condition %in% "31")],
                    y = FbRate.subj$VAS.mean[(FbRate.subj$Condition%in% "51")],
                    paired = TRUE, nullInterval = c(-Inf,0))

# noreward easy more pleasant than noreward hard ( >0 )
bf.noreward = ttestBF(x = FbRate.subj$VAS.mean[(FbRate.subj$Condition %in% "32")],
                      y = FbRate.subj$VAS.mean[(FbRate.subj$Condition %in% "52")],
                      paired = TRUE, nullInterval = c(0,Inf))


bf.reward
bf.noreward
```

# frequentist t-test, for relevant rate type (on averages across rate repetitions)
```{r}

# reward - pleasure
FbRate.subj.A = FbRate.subj[(FbRate.subj$RateType %in% "VASa"),]

t.reward.A = t.test(x = FbRate.subj.A$VAS.mean[(FbRate.subj.A$Condition %in% "31")],
                    y = FbRate.subj.A$VAS.mean[(FbRate.subj.A$Condition %in% "51")],
                    paired = TRUE, alternative = "less")
# reward - relief
FbRate.subj.R = FbRate.subj[(FbRate.subj$RateType %in% "VASr"),]

t.reward.R = t.test(x = FbRate.subj.R$VAS.mean[(FbRate.subj.R$Condition %in% "31")],
                    y = FbRate.subj.R$VAS.mean[(FbRate.subj.R$Condition %in% "51")],
                    paired = TRUE, alternative = "less")

# noreward - frustration (inverted)
FbRate.subj.F = FbRate.subj[(FbRate.subj$RateType %in% "VASf"),]

t.noreward.F = t.test(x = FbRate.subj.F$VAS.mean[(FbRate.subj.F$Condition %in% "32")],
                      y = FbRate.subj.F$VAS.mean[(FbRate.subj.F$Condition %in% "52")],
                      paired = TRUE, alternative = "greater")


t.reward.A
t.reward.R
t.noreward.F
```

# frequentist linear models
```{r}

#mLM.null = lmer(percent ~ 1 + (1 + RateType|Subject), data=expdata.FbRate, REML = FALSE)
# -> models with RateType as random effect do not converge

mLM.null = lmer(percent ~ 1 + (1 |Subject),
                data=expdata.FbRate, REML = FALSE)
mLM.outcome = lmer(percent ~ outcome + (1 |Subject),
                   data=expdata.FbRate, REML = FALSE)
mLM.efflev = lmer(percent ~ efflev + (1 |Subject),
                  data=expdata.FbRate, REML = FALSE)
mLM.maineffects = lmer(percent ~ outcome + efflev + (1 |Subject),
                       data=expdata.FbRate, REML = FALSE)
mLM.interaction = lmer(percent ~ outcome * efflev + (1 |Subject),
                       data=expdata.FbRate, REML = FALSE)
mLM.interactionNFC = lmer(percent ~ outcome * efflev * NFC + (1 |Subject),
                          data=expdata.FbRate, REML = FALSE)

anova(mLM.null, mLM.outcome, mLM.efflev, mLM.maineffects, mLM.interaction, mLM.interactionNFC)

anova(mLM.null, mLM.outcome)
anova(mLM.null, mLM.efflev)
anova(mLM.null, mLM.maineffects)
anova(mLM.null, mLM.interaction)
anova(mLM.null, mLM.interactionNFC)

anova(mLM.null, mLM.outcome)
anova(mLM.outcome, mLM.efflev)
anova(mLM.outcome, mLM.maineffects)
anova(mLM.outcome, mLM.maineffects)
anova(mLM.maineffects, mLM.interaction)
anova(mLM.outcome, mLM.interaction)
anova(mLM.interaction, mLM.interactionNFC)

# Forest-plot of estimates
plot_model(mLM.interactionNFC, type = "std2")
# random effects
plot_model(mLM.interactionNFC, type = "re")
# Marginal effects of interaction terms in model
plot_model(mLM.interactionNFC, type = "int")

p = interact_plot(mLM.interactionNFC, pred = "NFC", modx = "efflev", mod2 = "outcome",
                  interval = T, plot.points = F)
p + theme_classic()
```
```{r Age}
## Age

# subset
expdata.age = subset(expdata, select = c(Subject, Age))
# drop duplicates
expdata.age = expdata.age[!duplicated(expdata.age$Subject),]

# calculate median and range
age.subj = c(median(expdata.age$Age),range(expdata.age$Age))

```

```{r Doors.RESP}
## Doors.RESP - Door selection

# filter single entries of Doors.RESP
expdata.doorresp = expdata[!(expdata$SubTrial %in% c(2:10)),]

# set up data frame for by-group processing 
doorresp.subj = group_by(expdata.doorresp, Subject, Doors.RESP)

# calculate the summary metrics: count of door selection by sbj and door
doorresp.subj = summarise(doorresp.subj, 
                    doorresp.count = n()
                    )
# wide format
doorresp.subj = cast(doorresp.subj, Subject ~ Doors.RESP, value = "doorresp.count")
doorresp.subj
```


```{r RateX}
## RateX - Effort Task ratings

# filter RatingList
expdata.ETR = expdata[(expdata$Running.SubTrial. %in% "RatingList"),]

# compute VAS as percentage (relative to pixel range)
expdata.ETR$RateX = (expdata.ETR$RateX-316)/396*100

# set up data frame for by-group processing (RatingList = list of questions rated)
ETR.subj = group_by(expdata.ETR, Subject, RatingList)

# calculate the summary metrics: average of RateX by sbj and question
ETR.subj = summarise(ETR.subj, 
                         RateX.mean = mean(RateX)
                    )

# set up data frame for by-group processing (rating-list wise)
ETR.sum = group_by(ETR.subj, RatingList)
# calculate the summary metrics: average and SD if RateX across sbj
ETR.sum = summarise(ETR.sum, 
                        Rate.avg = mean(RateX.mean),
                        Rate.sd = sd(RateX.mean)
                    )


## stats on ETR (paired Bayesian t-tests)
# moeilijk easy lower than moeilijk hard ( <0 )
bf.ETR.moe = ttestBF(x = ETR.subj$RateX.mean[(ETR.subj$RatingList %in% "1")],
                y = ETR.subj$RateX.mean[(ETR.subj$RatingList %in% "2")],
                paired = TRUE, nullInterval = c(-Inf,0))
bf.ETR.moe
# aangenaam easy higher than aangenaam hard ( >0 )
bf.ETR.aan = ttestBF(x = ETR.subj$RateX.mean[(ETR.subj$RatingList %in% "3")],
                y = ETR.subj$RateX.mean[(ETR.subj$RatingList %in% "4")],
                paired = TRUE, nullInterval = c(0,+Inf))
bf.ETR.aan
# gedreven easy different than gedreven hard 
bf.ETR.ged = ttestBF(x = ETR.subj$RateX.mean[(ETR.subj$RatingList %in% "5")],
                y = ETR.subj$RateX.mean[(ETR.subj$RatingList %in% "6")],
                paired = TRUE)
1/bf.ETR.ged
# leuk easy different than leuk hard 
bf.ETR.leu = ttestBF(x = ETR.subj$RateX.mean[(ETR.subj$RatingList %in% "7")],
                y = ETR.subj$RateX.mean[(ETR.subj$RatingList %in% "8")],
                paired = TRUE)
1/bf.ETR.leu


# wide format
ETR.wide = cast(ETR.subj, Subject ~ RatingList, value = "RateX.mean")


# plot ETR

# whole question: labels=expdata.ETR$text[1:8]

# create variables defining question type and effort level
ETR.subj$qtype = rep(c("moeilijk", "aangenaam", "gedreven om correct", "leuk om correct"), each = 2)
ETR.subj$qtype = factor(ETR.subj$qtype,                                                              # force order
                        levels = c("moeilijk", "aangenaam", "gedreven om correct", "leuk om correct"))
ETR.subj$effort = rep(c("easy", "hard"))

# plot violin
ETR.subj %>%
  ggplot(aes(x = effort, y = RateX.mean)) +
  geom_point() +
  geom_violin(mapping = NULL, data = NULL, stat = "ydensity",
              position = "dodge", draw_quantiles = NULL, trim = TRUE,
              scale = "area", na.rm = FALSE, show.legend = NA, inherit.aes = TRUE) + 
  stat_summary(fun.y=mean, geom="point", shape=20, size=5) +
  geom_jitter(shape=16, position=position_jitter(0.02), size=1) +
  theme(axis.text = element_text(size = 16),
        axis.title = element_text(size = 16)) +
  facet_grid(. ~ qtype)

# plot geom line between effort levels for each sbj
ETR.subj %>%
  ggplot(aes(x = effort, y = RateX.mean, group = Subject)) +
  geom_point() +
  stat_summary(fun.y=mean, geom="point", shape=20, size=5) +
  theme(axis.text = element_text(size = 16),
        axis.title = element_text(size = 16)) +
  geom_line() +
  facet_grid(. ~ qtype)
```

```{r EffortResponse.ACC}
## EffortResponse.ACC

#filter EffortTaskList

expdata.acc = expdata[(expdata$Running.SubTrial. %in% "EffortTaskList"),]

# sort by sbj and cond
expdata.acc = expdata.acc[order(expdata.acc$Subject, expdata.acc$Condition),] 

# subset 
expdata.acc = subset(expdata.acc, select = c(Subject, Condition, EffortResponse.ACC))

# set up data frame for by-group processing 
expdata.acc = group_by(expdata.acc, Condition)


# calculate the summary metrics
acc.sum = summarise(expdata.acc, 
                                acc.mean = mean(EffortResponse.ACC),
                                acc.sd = sd(EffortResponse.ACC))


# plot accuracy with prob density

expdata.acc = expdata.acc[!(expdata.acc$Condition %in% c("32", "52")),] # filter out Condition = 32 52 (exclude conditions where effort task followed the rating)

acc.subj = group_by(expdata.acc, Condition, Subject) # set up data frame for by-group processing 

acc.subj = summarise(acc.subj,                      # calculate the summary metrics - mean for Subject*Condition
                    ACC.mean = mean(EffortResponse.ACC))

# plot expdata.acc

acc.subj$Condition = as.factor(acc.subj$Condition)

acc.subj$label = factor(acc.subj$Condition, 
                       labels=c("Easy", "Hard"))   


acc.subj %>%
  ggplot(aes(x = label, y = ACC.mean)) +
  geom_point() +
  geom_violin(mapping = NULL, data = NULL, stat = "ydensity",
              position = "dodge", draw_quantiles = NULL, trim = TRUE,
              scale = "area", na.rm = FALSE, show.legend = NA, inherit.aes = TRUE) + 
  stat_summary(fun.y=mean, geom="point", shape=20, size=5) +
  theme(axis.text = element_text(size = 16),
        axis.title = element_text(size = 16))

# stats on ACC (paired Bayesian t-test, one tailed)
# acc easy higher than acc hard ( >0 )
bf.acc = ttestBF(x = acc.subj$ACC.mean[(acc.subj$Condition %in% "22")],
                y = acc.subj$ACC.mean[(acc.subj$Condition %in% "42")],
                paired = TRUE, nullInterval = c(0,Inf))
bf.acc
```

```{r EffortResponse.RT}
## EffortResponse.RT


#filter EffortTaskList

expdata.RT = expdata[(expdata$Running.SubTrial. %in% "EffortTaskList"),]

# filter EffortResponse.ACC != 0 (exclude mistakes)

expdata.RT = expdata.RT[!(expdata.RT$EffortResponse.ACC %in% "0"),]


# sort by sbj and cond
expdata.RT = expdata.RT[order(expdata.RT$Subject, expdata.RT$Condition),] 

# subset 
expdata.RT = subset(expdata.RT, select = c(Subject, Condition, EffortResponse.RT))

# filter out Condition = 32 52 (exclude conditions where effort task followed the rating)
expdata.RT = expdata.RT[!(expdata.RT$Condition %in% c("32", "52")),]

# set up data frame for by-group processing 
RT.subj = group_by(expdata.RT, Condition, Subject)

# calculate the summary metrics - mean for Subject*Condition
RT.subj = summarise(RT.subj,
                         RT.mean = mean(EffortResponse.RT))

# calculate the summary metrics - mean for Condition (on within Subject average)
RT.sum = group_by(RT.subj, Condition)
RT.sum = summarise(RT.sum,
                   RT.avg = mean(RT.mean),
                   RT.sd = sd(RT.mean))

# stats on RTs (paired Bayesian t-test, one tailed)
# rt easy lower than rt hard ( <0 )
bf.RT = ttestBF(x = RT.subj$RT.mean[(RT.subj$Condition %in% "22")],
                y = RT.subj$RT.mean[(RT.subj$Condition %in% "42")],
                paired = TRUE, nullInterval = c(-Inf,0))
bf.RT

# plot RT

RT.subj$Condition = as.factor(RT.subj$Condition)

RT.subj$label = factor(RT.subj$Condition, 
                labels=c("Easy", "Hard"))  # excluded:  "EasyRating" , "HardRating"


RT.subj %>%
  ggplot(aes(x = label, y = RT.mean)) +
  geom_point() +
  geom_violin(mapping = NULL, data = NULL, stat = "ydensity",
            position = "dodge", draw_quantiles = NULL, trim = TRUE,
            scale = "area", na.rm = FALSE, show.legend = NA, inherit.aes = TRUE) +
  stat_summary(fun.y=mean, geom="point", shape=15, size=5, color="red") +
  geom_jitter(shape=16, position=position_jitter(0.02), size=2) +
  theme(axis.text = element_text(size = 16),
        axis.title = element_text(size = 16))
```